Revealing the Bound Nucleon 3D Partonic Structure through Incoherent Deeply Virtual Compton Scattering off $^4$He

### 2018-02-02 eg6-letters/incoherent/incoherent_prl.tex
update the incoherent plots
added the updated figure 2 and 3 in the incoherent channel with the source files
start writing the incoherent prl

\title{Incoherent Deep Virtual Compton Scattering off $^4$He using CLAS 
spectrometer}

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}

\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
 %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {R.~Dupr\'{e}} 
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {K.~Hafidi} 
\email[corresponding author: ]{kawtar@anl.gov}
\affiliation{\ANL}

\collaboration{The CLAS Collaboration}
\noaffiliation

%
\date{\today}
\begin{abstract}
We report the incoherent beam-spin asymmetry measurement of deeply virtual 
Compton scattering (DVCS) off $^4$He. The experiment used the 6 GeV electron 
beam from Jefferson Lab projected onto a $^4$He target in the center of the 
CEBAF Large Acceptance Spectrometer (CLAS).
\end{abstract}
\pacs{Valid PACS appear here}

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/ALU_phi_p_Q2.pdf}
\includegraphics[width=8.9cm]{figs/ALU_phi_p_x.pdf}
\includegraphics[width=8.9cm]{figs/ALU_phi_p_t.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel).  The error bars represent the statistical 
uncertainties. The gray bands represent the systematic uncertainties, including 
the normalisation uncertainties. The red curves are the results of our fits 
with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
\label{fig:alu}
\end{figure}

>>>>

\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent 
Deeply Virtual Compton Scattering off $^4$He}

\input author_list.tex

%
\date{\today}
\begin{abstract}
The three-dimensional imaging of the nucleon's fundamental partons, i.e, quarks 
and gluons, is set to be revealed through the generalized parton distributions 
(GPDs). While the majority of our knowledge about the nucleons' partonic 
structure has come from the elsatic and deep-inelastic lepton scatterings,

they have not resolved the question of how partons share the nucleon’s spin and 
build up its intrinsic properties, such as the mass and the electromagnetic 
properties. Understanding the correlations between the momentum and spatial 
degrees of freedom of the partons inside the nucleons is a powerful way to 
characterize the nucleons’ structure and resolve theses crucial open
questions. These correlations are accessible via the study of generalized 
parton distributions
(GPDs), which we probe with hard exclusive scattering reactions, such as 
deeply-virtual
Compton scattering (DVCS)

We report on the beam-spin asymmetry measurement associated with incoherent 
deeply virtual Compton scattering off $^4$He in the valence quark region.  The 
data has been accumulated using a 6 GeV longitudinally-polarized electron beam 
incident on a pressurized $^4$He gaseous target placed in front of CLAS 
spectrometer at Thomas Jefferson National Accelerator Facility. The base setup 
of CLAS detected the scattered electrons and the recoil protons, while the 
final-state real photons are detected by a supplementary electromagnetic 
calorimeter at very forward angles.  The measured incoherent beam-spin 
asymmetries indicate a suppression compared to those on free proton, indicating 
possible medium modifications on the nucleon's quark distributions and opening 
new opportunities to explore the origin of the EMC effect within the 
generalized parton distributions framework.

\end{abstract}
\pacs{Valid PACS appear here}

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel).  The error bars represent the statistical 
uncertainties. The gray bands represent the systematic uncertainties, including 
the normalisation uncertainties. The red curves are the results of our fits 
with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
\label{fig:alu}
\end{figure}
